Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels

### 2019-04-16 ICPP-19/communications.tex
minor

		With these $K_i$ tasks in place, the schedule on the computation
		resource contains $m$ slots of length exactly $b'$, in which all $A_i$
		tasks must fit without preemption. \todo[inline]{SKumar: It is not clear why it would be triplet}
		\todo[inline]{At each point in $S$, exactly one $K_i$ task is active, hence we define triplet $TR_{i+}$ as the set of tasks which complete their data transfers when $K_i$ task is in computation phase. As $C=b'+3$ and $S$ has no idle time on the communication resource, total computation time of tasks in $TR_{i+1}$ must not be more than $b'$. $S$ also has no idle time on the computation resource, therefore total computation time of tasks in $TR_i$ is exactly $b'$, and thus $a_{i_1} + a_{i_2} + a_{i_3} = b$. } We can thus define triplet $TR_i$
		as the set of tasks which execute during the communication phase of
		task $K_i$. Since at each point in $S$, exactly one $K_i$ task is
		active, and since $S$ has no idle time on the computation resource,
		the total computation time of tasks in $TR_i$ is exactly $b'$, and thus
		$a_{i_1} + a_{i_2} + a_{i_3} = b$. This partition is thus a valid
		solution for the \threepart instance $A$.

>>>>

		With these $K_i$ tasks in place, the schedule on the computation
		resource contains $m$ slots of length exactly $b'$, in which all $A_i$
		tasks must fit without preemption. \todo[inline]{SKumar: It is not clear why it would be triplet}
		\todo[inline]{At each point in $S$, exactly one $K_i$ task is active, hence we define triplet $TR_{i}$ as the set of tasks which complete their data transfers when $K_i$ task is in computation phase. As $C=b'+3$ and $S$ has no idle time on the communication resource, total computation time of tasks in $TR_{i}$ must not be more than $b'$. $S$ also has no idle time on the computation resource, therefore total computation time of tasks in $TR_i$ is exactly $b'$, and thus $a_{i_1} + a_{i_2} + a_{i_3} = b$. } We can thus define triplet $TR_i$
		as the set of tasks which execute during the communication phase of
		task $K_i$. Since at each point in $S$, exactly one $K_i$ task is
		active, and since $S$ has no idle time on the computation resource,
		the total computation time of tasks in $TR_i$ is exactly $b'$, and thus
		$a_{i_1} + a_{i_2} + a_{i_3} = b$. This partition is thus a valid
		solution for the \threepart instance $A$.
